Scheeper's Meager-NWD Game and the Menger Game

### 2014-11-17 phd/dissertation/chapter3.tex
symmetrize chapter names
polishing limited info results on bell's game
countable products result

\chapter{$W$ Convergence and Clustering Games}

@@

@@

\begin{defn}
  Let $\Sigma_{y} X^\kappa$ be a \term{sigma product} of $X$ with dimension
  $\kappa$ for each $y\in X^\kappa$, the subset of the usual Tychonoff
  product space $X^\kappa$ such that $x\in \Sigma_y X^\kappa$ if and only if
  $\{\alpha<\kappa : x(\alpha)\not=y(\alpha)\}$ is countable.

  For homogeneous spaces $X$ containing $0$, $y$ is usually assumed to be the
  zero vector $\vec 0$ and the sigma product is written $\Sigma X^\kappa$.
\end{defn}

>>>>

\chapter{Gruenhage's Convergence and Clustering Games}

@@

\begin{prop} For any $x\in X$ and $k<\omega$,
  \begin{itemize}
    \item
      $
      \pl O\ktactwin{k+1}\gruConGame{X}{x}
        \Leftrightarrow
      \pl O\tactwin\gruConGame{X}{x}
      $
    \item
      $
      \pl O\kmarkwin{k+1}\gruConGame{X}{x}
        \Leftrightarrow
      \pl O\markwin\gruConGame{X}{x}
      $
  \end{itemize}
\end{prop}

\begin{proof}
  If $\sigma$ witnesses $\pl O\ktactwin{k+1}\gruConGame{X}{x}$,
  let $\tau(\emptyset)=\sigma(\emptyset)$ and
    \[
      \tau(\<q\>)
        =
      \bigcap_{i< k}
      \sigma(\<\underbrace{x,\dots,x}_{k-i},q,\underbrace{x,\dots,x}_{i+1}\>)
    \]

  Then $\tau$ is easily verified to be a winning tactic, and
  the proof for the second part is analogous.
\end{proof}

@@

\begin{defn}
  Let $\Sigma_{y} \prod_{\alpha<\kappa}X_\alpha$ be a \term{sigma-product} of
  $X$ with dimension $\kappa$ for each $y\in \prod_{\alpha<\kappa}X_\alpha$,
  the subset of the usual Tychonoff product space $\prod_{\alpha<\kappa}X_\alpha$
  such that $x\in \Sigma_y \prod_{\alpha<\kappa}X_\alpha$
  if and only if $\{\alpha<\kappa : x(\alpha)\not=y(\alpha)\}$ is countable.

  Unless otherwise specified, we assume $0\in X_\alpha$ for all $\alpha<\kappa$
  and $y=\vec 0$, and write $\Sigma \prod_{\alpha<\kappa}X_\alpha$.
\end{defn}
